ODGI: understanding pangenome graphs

### 2021-08-11 manuscript/main.tex
authors

\title[short Title]{ODGI: tools for working with pangenome graphs}
\author[Heumos, \textit{et~al}.]{
Simon Heumos\,$^{\text{\sfb 1, \sfb 2} \dagger}$,
Andrea Guarracino\,$^{\text{\sfb 2} \dagger}$,
Pjotr Prins\,$^{\text{\sfb 3}}$,
and Erik Garrison\,$^{\text{\sfb 3}*}$
}

\address{
$^{\text{\sf 1}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076
$^{\text{\sf 2}}$University of Tor Vergata, Rome, Italy and \\
$^{\text{\sf 3}}$University of Tennessee Health Science Center, Memphis, TN, USA
}

>>>>

\title[short Title]{ODGI: understanding pangenome graphs}
\author[Heumos, \textit{et~al}.]{
Andrea Guarracino\,$^{\text{\sfb 1} \dagger}$,
Simon Heumos\,$^{\text{\sfb 2} \dagger}$,
Pjotr Prins\,$^{\text{\sfb 3}}$,
and Erik Garrison\,$^{\text{\sfb 3}*}$
}

\address{
$^{\text{\sf 1}}$University of Tor Vergata, Rome, Italy and \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076
$^{\text{\sf 3}}$University of Tennessee Health Science Center, Memphis, TN, USA
}
